Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-16 manuscript.Rmd
polished graphs

## Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement, generated from analysis-part2 -->

```{r}

>>>>

## Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement, generated from analysis-part2 -->
```{r}
# Count up position totals and join into an agreement data frame
calculate_agreement <- function(ds) {
  model <- ds %>% count(file, pos) %>% add_count(file, wt = n, name = "total") %>% mutate(prop_model = n/total)
  human <- ds %>% count(file, code) %>% add_count(file, wt = n, name = "total") %>% mutate(prop_human = n/total)
  agree_group <- full_join(select(model, file, pos, prop_model), 
                     select(human, file, code, prop_human), 
                     by = c("file" = "file", "pos" = "code"))
  agree_group <- agree_group %>% mutate(prop_human = ifelse(is.na(prop_human), 0, prop_human),
                            prop_model = ifelse(is.na(prop_model), 0, prop_model))
  agree_group <- complete(agree_group, file, pos, fill = list(prop_human = 0, prop_model = 0))
}

agreement_scatter <- function(ds) {
  ggplot(ds) +
  geom_point(aes(x = prop_human, y = prop_model, fill = pos), shape = 21, alpha = .5, size = 4) + 
  geom_abline(intercept = 0, slope = 1) + 
  scale_fill_manual(name = "Posture", values = pal, guide = "none") + 
  scale_x_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Actual Prevalence (%)") + 
  scale_y_continuous(breaks = c(0,.5,1), labels = c(0, 50, 100), limits = c(-.07, 1.07), name = "Predicted Prevalence (%)") + 
  facet_wrap("pos", ncol = 2, as.table = F) +
  theme(panel.spacing.x = unit(1, "lines")) +
  theme(panel.spacing.y = unit(1, "lines")) + 
  theme(strip.background = element_blank(), strip.text.x = element_text(size = 16, face = "bold"))
}
```

```{r part2overall, warning=FALSE, fig.cap="Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant.", fig.align="center", fig.width=7, fig.height=6.7}
# GROUP MODEL PART 2 AGREEMENT
pt2_group <- read_csv("data/compiled_agreement_position.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels))
pt2_split <- read_csv("data/compiled_agreement_split.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels))

agree <- map(list("group" = pt2_group, "split" = pt2_split), calculate_agreement)

group_agree_cor <- cor_test(agree$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree$split, vars = c("prop_model", "prop_human")) %>% pull(cor)

agree_plots <- map(agree, agreement_scatter)
agree_plots <- map2(agree_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))

agree_plots[[1]] + agree_plots[[2]]
```

### 2023-02-16 manuscript.tex
polished graphs

\hypertarget{current}{%
\section{Current}\label{current}}

@@

\hypertarget{goal-1-optimize-and-validate-body-position-classification-model}{%
\section{Goal 1: Optimize and validate body position classification model}\label{goal-1-optimize-and-validate-body-position-classification-model}}

\hypertarget{goal-2-assess-classification-accuracy-across-a-long-delay}{%
\section{Goal 2: Assess classification accuracy across a long delay}\label{goal-2-assess-classification-accuracy-across-a-long-delay}}

\hypertarget{goal-3-examine-wear-time-and-compliance-in-full-day-data-collection}{%
\section{Goal 3: Examine wear time and compliance in full-day data collection}\label{goal-3-examine-wear-time-and-compliance-in-full-day-data-collection}}

\hypertarget{goal-4-compare-classification-estimates-to-prior-literature}{%
\section{Goal 4: Compare classification estimates to prior literature}\label{goal-4-compare-classification-estimates-to-prior-literature}}

>>>>

\hypertarget{current-study}{%
\section{Current Study}\label{current-study}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{goal-1-optimize-and-validate-body-position-classification-model}{%
\subsection{Goal 1: Optimize and validate body position classification model}\label{goal-1-optimize-and-validate-body-position-classification-model}}

\hypertarget{goal-2-assess-classification-accuracy-over-long-recordings}{%
\subsection{Goal 2: Assess classification accuracy over long recordings}\label{goal-2-assess-classification-accuracy-over-long-recordings}}

\begin{figure}

{\centering \includegraphics{manuscript_files/figure-latex/part2overall-1}

\caption{Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant.}\label{fig:part2overall}
\end{figure}

\hypertarget{goal-3-compare-classification-estimates-to-prior-literature}{%
\subsection{Goal 3: Compare classification estimates to prior literature}\label{goal-3-compare-classification-estimates-to-prior-literature}}

\hypertarget{goal-4-examine-wear-time-and-compliance-in-full-day-data-collection}{%
\subsection{Goal 4: Examine wear time and compliance in full-day data collection}\label{goal-4-examine-wear-time-and-compliance-in-full-day-data-collection}}
